Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
start box1

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a social distance threshold, to define social associations. We
found increasing individual graph strength across three habitat layers with
increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
habitat layers differed in their response to social distance threshold, with
open and foraging with a larger increase in graph strength and greater variation
across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.

@@

>>>>

@@

# Box 1
Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a social distance threshold, to define social associations. We
found increasing individual graph strength across three habitat layers with
increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
habitat layers differed in their response to social distance threshold, with
open and foraging with a larger increase in graph strength and greater variation
across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.
